Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-02 overleaf/results.tex
Minor edits to results.

We conjecture that MPC Source, a straight-forward representation suitable for static analysis, will not only enable detection of general associative loops, but also allow 
for program synthesis to increase opportunities for divide-and-conquer parallelization~\cite{Farzan:2021}; we leave this as future work.

>>>>

We conjecture that MPC Source, a straight-forward representation suitable for static analysis, will not only enable detection of general associative loops, but also allow 
for program synthesis to increase opportunities for divide-and-conquer parallelization~\cite{Farzan:2021}; we leave this and other optimizations as future work.
